---
title: "Modeling and prediction for movies"
author: "Neal Yu"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
```

### Load data

```{r load-data}
load("movies.Rdata")
```



* * *

## Part 1: Data
Looks like the data was collected through observational study. Since all the 651
movies are randomly sampled, the generalibility target can be achieved. Also, because
there is no controled experiment thus no random assignment applied, any causality
related conclusion may be reserved.

* * *

## Part 2: Research question
#### What similarities are among popular movies (good rating)?
* For audience, it might be helpful for them to select movies to watch.
* For movie producer, it can help them to make more popular movies via tuning some
of the features.


* * *

## Part 3: Exploratory data analysis

```{r dependent variable}

```


* * *

## Part 4: Modeling

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 5: Prediction

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 6: Conclusion

